Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-30 rnni_convexity.tex
add leaf labels fig 4 (merge-sort-split)

\begin{figure}[H]
\centering
\includegraphics[width=.8\textwidth]{NNI_NP_proof}
\vspace{12pt}
\caption{Example of a shortest path between two trees $T$ and $R$ in $\nni$.
In \autocite{Li1996-zw} it is proven that there is a labelling that ensures that there is no shortest path in $\nni$ where the clusters (dots vs.\ squares) shared between $T$ and $R$ are preserved.
Instead, the depicted path where $\frac{n}{2}$ cherries are built and then sorted before being resolved is a shortest path}
\label{fig:NNI_NP_proof}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=.8\textwidth]{NNI_NP_proof}
\vspace{12pt}
\caption{Example of a shortest path between two trees $T$ and $R$ in $\nni$.
In \autocite{Li1996-zw} it is proven that there is a labelling that ensures that there is no shortest path in $\nni$ where the clusters $\{1, \ldots, m\}$ and $\{m+1, \ldots, n\}$ with $m = \frac{n}{2}$ shared between $T$ and $R$ are preserved.
Instead, the depicted path where $\frac{n}{2}$ cherries are built and then sorted before being resolved is a shortest path}
\label{fig:NNI_NP_proof}
\end{figure}
